---
title: "mtcars Multivariate Regression Model Builder"
author: "Danny Beery"
date: "2022-11-07"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## What is mtcars Multivariate Regression Model Builder?

A free to use tool for assessing how selecting predictors influences beta-coefficients and confidence intervals around predictors in a sample data set (mtcars).

## What is mtcars?

- mtcars is a publically available dataset that comes with base R

- mtcars contains on 11 variable for 32 automobiles

- mtcars variables include:
  <font size="3">
  - mpg (miles per gallon) 
  - cyl (# of cylinders)
  - disp (displacement)
  - hp (gross horsepower)
  - drat (real axle ratio)
  - wt (weight)
  - qsec (1/4 mile time)
  - vs (Engine: v-shaped or straight)
  - am (Transmission: automatic or manual)
  - gear (# of forward gears)
  - carb (# of carburetors)
  
  </font>
  
## Why?

- Many students do not know how important model selection can be when building multivariate Regression Models. 

- This tool can illustrate how not controlling for predictors can lead to statistically significant beta-coefficients.  

## Outputs

- This tool provides the beta coefficients of each predictor in order from top to bottom. 

- 95% confidence intervals for each predictor included.

## How to use 
<font size="2">

1. Check boxes to add predictors (The response variable has been automatically set as 'mpg').

2. Press Submit!

#### Example: Check boxes "Include/Exclude Wt" and "Include/Exclude am" only and press Submit.

</font>

```{r, echo = TRUE}
y <- lm(mpg ~ wt + am, data = mtcars)
coef(y)
confint(y)
```


## Insights

-Experiment with including and excluding predictors. 

-Notice how the beta coefficients and confidence intervals change!

